\ripple: Differentiable Waveforms for Gravitational Wave Data Analysis

### 2022-11-22 src/tex/ms.tex
added some words in fitting coefficients

\te{Kelvin should add stuff here}

@@

Every waveform approximants have some fitting parameters that are fixed during
the process of calibrating the ansatz to NR waveforms. In the case of
IMRPhenomD, there are $\sim 220$ \kw{Kelvin check number} fitting parameters
used to capture the behavior of the amplitude and phase as a function of the
mass ratio and spins. \kw{Say something about how the fitting parameters affect the accuracy of the waveform model}

@@

@@

\kw{Describe figure loss_compare}

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{../static/amplitude_loss.pdf}
\caption{ Relative error of amplitudes of IMRPhenomD waveforms. Blue: Error
    between original Phenom waveform and NR waveform; Orange: Error between
    optimized waveform and NR waveform. }
\label{fig:loss_compare}
\end{figure}

\kw{Describe figure logdiff}

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{../static/MM_logdiff_q148.pdf}
\caption{ Distribution of the log difference of mismatches between optimized
    and original model. The mean shows a 36\% decrease in mismatch. }
\label{fig:MM_logdiff}
\end{figure}

\kw{Describe implication}

% Implication

>>>>

% \te{Kelvin should add stuff here}

@@

Every waveform approximants have some fitting coefficients that are fixed during
the process of calibrating the ansatz to NR waveforms. In the case of 
IMRPhenomD, there are 209 fitting coefficients used to capture the separate behavior of 
the amplitude and phase as a function of the mass ratio and spins. 
\kw{Say something about how the fitting parameters affect the accuracy of the waveform model}

@@

Previously in the construction of IMRPhenomD \citep{Khan:2015jqa}, waveform coefficients are fitted in segments with amplitude and phase separated. 
Individual segments are then connected together such that they are differentiable. 
Using this method, the generated waveforms are expected to be erroneous, as the connections would affect the originally fitted segments. 
Hence, coefficients of the current IMRPhenomD implementation are often hand tuned in the final procedure. 
The set of coefficients are both is expensive and time-costly to calculate, and not the best-fitted solution. 
Instead, by joint fit, all coefficients are simultaneously fitted without having issues discussed above. 
Therefore, it is essential to fit the waveform jointly.

@@

\kw{Describe figure loss_compare}
Here, we define the mismatch as
\begin{equation}
	\mathcal{M}=1-\mathrm{m}(h_{\mathrm{IMR}}|h_{\mathrm{NR}}), 
\end{equation} 
In our optimization procedure, we took NR waveforms stated in \citep{Khan:2015jqa} as training waveforms to fit waveform coefficients. 
By defining the mean of individual mismatches as the loss function for optimization, we can calibrate the set of coefficients using gradient descent.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{../static/amplitude_loss.pdf}
\caption{Relative error of amplitudes of IMRPhenomD waveforms. Blue: Error
    between original Phenom waveform and NR waveform; Orange: Error between
    optimized waveform and NR waveform. }
\label{fig:loss_compare}
\end{figure}

\kw{Describe figure logdiff}
As demonstration, Fig. \ref{fig:loss_compare} shows the relative error of original and optimized waveform at different frequencies. 
In general, the error of optimized waveform is lower than that of the original waveform. 
The error in the early inspiral region is substantially decreased by half and other regions also show good improvement in accuracy.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{../static/MM_logdiff_q148_LIGO.pdf}
\caption{Distribution of the log difference of mismatches between optimized
    and original model. The mean shows a 36\% decrease in mismatch. }
\label{fig:MM_logdiff}
\end{figure}

Instead of examining individual waveforms, we investigate the general behavior of mismatches for a set of testing waveforms. 
In Fig. \ref{fig:logdiff_q148}, the distribution of log difference of mismatches are shown. 
The distribution mean lies towards the negative side, which indicates a improvement in the model. 
Despite there are testing waveforms that performed worse after optimization, it is verified that the ansatz of IMRPhenomD does not fit well with most of these waveforms, hence cannot be improved by optimization.  
Therefore, the new set of waveform coefficients can produce better waveforms for GW analyses.

\kw{Describe implication}
% Implication

With further modifications to the optimization process, the set of waveform coefficients can be retuned to give almost an order-of-magnitude improvement. 
Utilizing AD, differentiable waveform models can be further improved easily and quickly using similar computational schemes. 
Moreover, in the construction of new waveform models, AD shows significant advantages during their calibrating process.
